\documentclass[preprint,aps,nofootinbib,a4paper,superscriptaddress,longbibliography,amsfonts,amssymb,amsmath,titlepage]{revtex4-2}
\usepackage{IEEEtrantools}
\usepackage{microtype}
\usepackage[toc,title,page,titletoc]{appendix}
%\usepackage[pdftex]{hyperref}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\usepackage{mathbbol}


\newtheorem{definition}{Definition}

\begin{document}
\title{Tennis match forecasting; how AI can beat book makers on their own platforms}

\author{Patrick Schall}
\email{patrick.schall@gmail.com}

\author{Vahid Toomani}
\email{vahidtoomani2002@gmail.com}

\date{\today}

\maketitle
\tableofcontents

\newpage

\section{Introduction}
Intro:
\begin{itemize}
\item Context of the project's integration into your business.
\item From a technical point of view.
\item From an economic point of view.
\item From a scientific point of view.
\end{itemize}

\subsection{International tournaments and book makers}
ATP, Pinnacle sports, Bet 365

\subsection{Elo system}
Elo rate

\subsection{objectives}
Goals
\begin{itemize}
\item What are the main objectives to be achieved? Describe in a few lines.
\item For each member of the group, specify the level of expertise around the problem addressed?
\item Have you contacted business experts to refine the problem and the underlying models? If yes, detail the contribution of these interactions.
\item (Are you aware of a similar project within your company, or in your entourage? What is its progress? How has it helped you in the realization of your project? How does your project contribute to improving it?).
\end{itemize}

\section{Exploratory data analysis (EDA)}


\subsection{Data fetch}
source

\subsection{Data enrichment \& cleaning}
Which parts of data dropped or added?

\subsection{Data statistics and visualisations}
Put graphs and statistics of the data here.

\subsection{Strategies}
Strategies

\subsection{Feature selection}

\section{ML models and learning}


\subsection{Model selection}


\subsection{Random forest}


\subsection{Ada boost}


\subsection{Support vector Mmachine}


\subsection{Voting}


\subsection{Dense neural network}

\section{Post learning analysis \& packaging}


\subsection{Uncertainty cutoff}


\subsection{Cutoff optimization}


\section{Conclusion}

%\begin{thebibliography}{9}
%\bibitem{Aksteiner:2016mol}
%S.~Aksteiner and T.~B\"ackdahl,
%``Symmetries of linearized gravity from adjoint operators,''
%J. Math. Phys. \textbf{60} (2019) no.8, 082501
%doi:10.1063/1.5092587
%[arXiv:1609.04584 [gr-qc]].
%\end{thebibliography}
\end{document}